CS6213 Project Report

### 2021-05-07 report/paper.tex
Edits

Despite our experience, we are quite hopeful about Apalache's future prospects.
%
A more intelligent translation to SMT is likely to produce good results---SMT solvers have shown themselves very capable of tackling search problems in other domains.

>>>>

Despite our experience, we are hopeful about Apalache's prospects.
%
A more intelligent translation to SMT might produce good results---SMT solvers have shown themselves very capable of tackling search problems in other domains.
